Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-25 cav2017/cav2017.tex
small edit objectives

\item[RQ1] \textbf{(CEGIS)} do the CEGIS with multi-stage 
verification and abstraction refinement generate a FWL digital 
controller in a reasonable amount of time?

>>>>

\item[RQ1] \textbf{(CEGIS)} do the CEGIS with multi-stage 
verification and abstraction-based generate a FWL digital 
controller in a reasonable amount of time?
